---
title: "Final HRV"
author: "Brian Wright"
date: "October 11, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
setwd("C:/Users/bwright/Documents/R/VR/SessionData/vr")

```


```{r}
test <- read.csv()

library(dplyr)
library(stargazer)
library(spectral)

```

Need to build a script that calculates the seconds backwards to captures the bottom 120 seconds and generate the % of spectrum density inside the band between .04 and .15 as a % of the remaining spectrum, this becomes the relative power density inside that band. Also need to systematic sample every .05 seconds. 

We will then compared distributions of mobile versions non-mobile. Below are the individual operations now need to included in the function. 

```{r,eval=FALSE}
#File names for future argument 
vr_fileNames <- list.files(path="C:/Users/bwright/Documents/R/VR/SessionData/vr", pattern = "csv")

setwd("C:/Users/bwright/Documents/R/VR/SessionData/vr")

#1.Load Data
test_vr <- read.csv("gw1501_20170824123722.csv")
#View(test_vr)


#2.Calculates the difference between the rows
test_vr$diff <-  c(0,diff(test_vr$time))

#View(test_vr)

#3.Calculates the cumulitive sum in reverse. 
test_vr$cum_diff <- rev(cumsum(rev(test_vr$diff))) #double reverse. 

#View(test_vr)

#4.Next Step is identifying 120 in the cum_diff along the way and deleting everything else. 

subset_120 <- subset(test_vr, cum_diff <= 120)
#So I think all we need to do here in order to systematically sample is create a subset on the cum_diff column indicating a range to sample starting with between .05 and .01

#View(subset_120)

#New 5a. Sample entries between .05 and .1., runs the same
subset_120 <- subset(subset_120, subset_120$diff >= 0.050  & subset_120$diff <=.0599)

#str(subset_120)

dim(subset_120)
#5b.Then run the spectrum analysis on hr as seen below, just need to automate all this into a argument. 

#6.Generate the spectrum ----changed this in the testing process------ok changed back 11.26
spec_120_freq <- spectrum(subset_120$hr, method = "pgram")

#str(spec_120_freq)

#7.Generate dataframe composed of freq and spec output
spec_120_freq_df <- data.frame(spec_120_freq$freq,spec_120_freq$spec)
View(spec_120_freq_df)

#8.Subset based on LF freq
new_df = data.frame(subset(spec_120_freq_df, spec_120_freq_df$spec_120_freq.freq >= 0.04 & spec_120_freq_df$spec_120_freq.freq <= 0.15))

#9 Calculate Relative Power
LF_Power <- sum(new_df$spec_120_freq.spec)/sum(spec_120_freq_df$spec_120_freq.spec)

#10 Write the results to a list or data.frame
LF_Power

```

```{r, eval=FALSE}
#Creates the function to determine the power spectrum density 

lh_spec_cal <- function(i){
  i$diff <-  c(0,diff(i$time))
  i$cum_diff <- rev(cumsum(rev(i$diff)))
  sub_set <- subset(i, cum_diff <= 120)
  sub_set <- subset(sub_set, sub_set$diff >=.05 & sub_set$diff <=.075) 
  spec <- spectrum(sub_set$hr,method = "pgram")
  xxx <- data.frame(spec$freq,spec$spec)
  xxxx <- data.frame(subset(xxx, xxx$spec.freq >= .04 & xxx$spec.freq <= 0.15))
  relative <- subset(xxx,xxx$spec.freq < .04)
  LF_Power <- sum(xxxx$spec.spec)/(sum(xxx$spec.spec)-sum(relative$spec.spec))
  LF_Power
}

lh_spec_cal(test_vr)

#Create a list of file names
setwd("C:/Users/bwright/Documents/R/VR/SessionData/vr")

vr_fileNames <- list.files(path="C:/Users/bwright/Documents/R/VR/SessionData/vr", pattern = "csv")

#Run a loop to pass all the file names for vr
for (i in 1:length(vr_fileNames)) {
    vr <- read.csv(vr_fileNames[i], stringsAsFactors = FALSE)
    vr_output[i] <- lh_spec_cal(vr)
    vr_lh <- data.frame(vr_fileNames,vr_output)
}

#View(vr_lh)
median(vr_lh$vr_output)


#Ok now just need to do the same for the mobile device 

setwd("C:/Users/bwright/Documents/R/VR/SessionData/mobile")

mobile_filenames <- list.files(path="C:/Users/bwright/Documents/R/VR/SessionData/mobile", pattern = "csv")

mbl_output_1 <- (1:100)

#Run a for loop to pass all the file names for mobile
for (i in 1:length(mobile_filenames)) {
    mbl_1 <- read.csv(mobile_filenames[i], stringsAsFactors = FALSE)
    mbl_output_1[i] <- lh_spec_cal(mbl_1)
}

mbl_lh <- data.frame(mobile_filenames,mbl_output_1)

median(mbl_output_1)



```


testing...
```{r, eval=FALSE}
test_vr$diff <- c(0,diff(test_vr$time))
head(test_vr$diff)
test_vr$cum_diff <- rev(cumsum(test_vr$diff))
head(test_vr)
sub_set <- subset(test_vr, cum_diff <=120)
head(sub_set)

spec <- spectrum(sub_set$hr, method = "ar")
xxx <- data.frame(spec$freq, spec$spec)
View(xxx)
View(xxxx)
xxxx <- data.frame(subset(xxx, xxx$spec.freq >= .04 & xxx$spec.freq <= 0.15))

head(xxxx)
head(xxx)

relative <- subset(xxx,xxx$spec.freq < .04)
View(relative)


LF_Power <- sum(xxxx$spec.spec)/(sum(xxx$spec.spec)-sum(relative$spec.spec))
LF_Power

head(sub_set)
```
Basic descripitive stats
```{r}
library(dplyr)
library(doBy)
setwd("C:/Users/bwright/Documents/R/VR/")

pb_data <- read.csv("VR_Data2.csv") #dataframe containing all the output from the 220 sessions
str(pb_data)

xx <- summaryBy(time~UserType, pb_data) #Generating the time averages for the two groups. 

xx



```

